Preliminary (quick and dirty) results

### 2022-10-13 slides/data_checking.Rmd
catching up on much older work history

---
title: "Exploratory data analysis"
subtitle: "J-Study"
author: "Monica Thieu & Lauren Wilkins"
institute: "Columbia University Dept of Psychology"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["theme.css", "fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      dev = "svglite",
                      message = FALSE,
                      warning = FALSE,
                      fig.asp = 7/10)

@@

### What is the age and gender breakdown?

@@

### What is our sample spread of trivia expertise?

@@

### Are men and women participants balanced on trivia expertise?

@@

### Do older participants know more trivia?

@@

### Do Ps accurately assess their own trivia skill?

@@

### Trivia recall by confidence

@@

### Metamemory state counts (correct trials only!)

@@

### Recall accuracy by metamemory state

@@

### Metamemory state relative percentages

@@

### How many people got which categories?

@@

### Are some categories more interesting than others?

@@

### Are trivia experts more interested overall?

@@

### Fact recall by question order/chunk type

@@

### Fact recall by chunk type

@@

### Is recall higher when people already know (some of) the facts?

@@

### Photo recognition

@@

### Source memory for which museum

@@

### Source memory for which museum

@@

### Does _photo_ retrieval predict _fact_ retrieval?

@@

### Does _photo_ retrieval predict _fact_ retrieval?

@@

### Does _source_ retrieval predict _fact_ retrieval?

@@

### Does _source_ retrieval predict _fact_ retrieval?

@@

### Does _source_ retrieval predict _photo_ retrieval?

@@

### Does _source_ retrieval predict _photo_ retrieval?

@@

### Does interest at encoding predict _fact_ retrieval?

@@

### Does interest at encoding predict _photo_ retrieval?

@@

### Does interest at encoding predict _source_ retrieval?

>>>>

---
title: "Exploratory data analysis"
subtitle: "J-Study"
author: "Monica Thieu & Lauren Wilkins"
institute: "Columbia University Dept of Psychology"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

@@

What is the age and gender breakdown?

@@

What is our sample spread of trivia expertise?

@@

Are men and women participants balanced on trivia expertise?

@@

Do older participants know more trivia?

@@

Do Ps accurately assess their own trivia skill?

@@

## Trivia recall by confidence

@@

## Trivia recall metamemory

Metamemory state counts (correct trials only!)

@@

Recall accuracy by metamemory state

@@

Metamemory state relative percentages

@@

How many people got which categories?

@@

Are some categories more interesting than others?

@@

Are trivia experts more interested overall?

@@

## Fact recall by question order/chunk type

@@

## Fact recall by chunk type

@@

## Is recall higher when people already know (some of) the facts?

@@

## Photo recognition

@@

## Source memory for which museum

@@

@@

## Does _photo_ retrieval predict _fact_ retrieval?

@@

@@

## Does _source_ retrieval predict _fact_ retrieval?

@@

@@

## Does _source_ retrieval predict _photo_ retrieval?

@@

@@

## Does interest at encoding predict _fact_ retrieval?

@@

## Does interest at encoding predict _photo_ retrieval?

@@

## Does interest at encoding predict _source_ retrieval?

### 2022-10-13 slides/results.Rmd
catching up on much older work history

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         j_score = j_score - 0.7,
         interest = (interest / 100) - 0.5) %>% 
  lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

>>>>

# Proposed main figures

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # scaled to units of 0.1
         j_score = (j_score - 0.7) * 10,
         interest = (interest / 100) - .5) %>% 
  lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         across(c(resp_pic, resp_source), ~(. / 100)),
         interest = (interest / 100) - 0.5,
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + interest + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

### _Combined_ recognition predicts _fact_ recall, slightly more so for experts

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         resp_either = resp_pic + resp_source,
         acc_recall = as.integer(acc_recall > 0)) %>%
  filter(resp_either > 0) %>% 
  group_by(subj_num, j_score, resp_either) %>%
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = resp_either, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_smooth(method = "lm", alpha = 0.2) + 
  scale_x_continuous(breaks = 1:2) +
  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  labs(x = "Joint associate recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme_bw()
```

### _Combined_ recognition predicts _fact_ recall, slightly more so for experts

Formula: `acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num)`

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         # so, like 20% of participants have no retrieval trials where they missed on both source and pic
         # so this is run only using trials where people got _either_ source _or_ pic
         # aka the difference between getting one and getting both
         resp_either = resp_pic + resp_source - 1,
         j_score = j_score - 0.7) %>% 
  filter(resp_either > -1) %>% 
  lme4::glmer(acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```
